\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Neranjan Marasinghe} % Your name
% You can merge both of these into a single line, if you do not have a website.

\address{Math 106 B, Lubbock, TX, 79409}
\address{Email: \href{mailto:nemarasi@ttu.edu}{nemarasi@ttu.edu}}
\address{Texas Tech University, Department of Mathematics and Statistics} 

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\medskip 

\begin{rSection}{Education}

{\bf Texas Tech University}\hfill{ Lubbock, TX, USA}
\\ \textit{PhD student in Mathematics (Advisor : Prof. Alexander Solynin)} \hfill{\em \scriptsize{Aug 2021 - May 2026} }
\\ \textit{GPA : 4.00/4.00}

{\bf University of Peradeniya}\hfill{Peradeniya, Sri Lanka}
\\ \textit{BSc in Electrical and Electronics Engineering} \hfill{\em \scriptsize{Nov 2014 - Jan 2019} }
\\ \textit{GPA : 3.60/4.00}



\end{rSection}


%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Interests}

{\bf  Complex Analysis} : Potential Theory, Symmetrization, Geometric Function Theory, Complex Dynamics
\end{rSection}

\begin{rSection}{Experience}

{\bf Texas Tech University, Department of Mathematics and Statistics}\hfill{\em Lubbock, TX, USA}
\\ \textit{Graduate Part Time Instructor} \hfill{\em Fall 2022-Fall 2023 }

{\bf Texas Tech University, Department of Mathematics and Statistics}\hfill{\em Lubbock, TX, USA}
\\ \textit{Research Assistant} \hfill{\em Summer 2022 }

{\bf Texas Tech University, Department of Mathematics and Statistics}\hfill{\em Lubbock, TX, USA}
\\ \textit{Teaching Assistant} \hfill{\em Fall 2021, Spring 2022 }


{\bf University of Peradeniya, Department of Engineering Mathematics} \hfill {\em Peradeniya, Sri Lanka}
\\\textit{Teaching Assistant} \hfill {\em March 2019 - August 2021}




{\bf Huawei Technologies (Pvt.) Ltd. } \hfill {\em Colombo, Sri Lanka}
\\\textit{Trainee Electrical and Electronics Engineer } \hfill {\em Oct. 2017 - Jan. 2018 }


{\bf Milco (Pvt.) Ltd.} \hfill {\em Ambewela, Sri Lanka}
\\\textit{Trainee Electrical and Electronics Engineer } \hfill {\em Oct. 2016 - Jan. 2017 }


\begin{rSection}{Teaching}

\textbf{At Texas Tech University} 
\begin{itemize}
    \item MATH 1321 Trigonometry(Fall 2022)
    \newline \url{https://www.youtube.com/playlist?list=PLTZv4jL4go4RQc1WdhkGjOS6BeAEtdJPQ} 
    \item MATH 1452 Calculus II (Spring 2023)
    \newline \url{https://www.youtube.com/playlist?list=PLTZv4jL4go4Q75HmF68qLb7AqOrOUjlJ6}
    \item MATH 3350 Higher Mathematics for Scientists and Engineers (Summer 2023)
    \newline \url{https://www.youtube.com/playlist?list=PLTZv4jL4go4S0VJdLFm0p4qdiPkFiqj9N}

    \item MATH 1451 Calculus I (Fall 2023)
    \newline \url{https://www.youtube.com/playlist?list=PLTZv4jL4go4SiR4zn_RIRFLHYoi8643H6}
\end{itemize}

\medskip

\textbf{At University of Peradeniya}
\begin{itemize}
    \item GP 116 - Linear Algebra (2019 Semester 02, 2020 Semester 02)
    \newline \url{https://www.youtube.com/watch?v=QRd-jd6j2rs&list=PLTZv4jL4go4QUKES6N3Okgj0TXCjJuwut}
    \item GP 115 - Calculus I (2019 Semester 01, 2021 Semester 01)
    \item EM 505 - Complex Analysis (2021 Semester 02)
    \item EM 316 - Numerical Methods for Electrical and Electronics Engineers (2019)
    \item EM 215 - Numerical Methods (2020)
\end{itemize}
\medskip

\textbf{YouTube Teaching}
\begin{itemize}
    \item Complex Analysis\\
\url{https://www.youtube.com/playlist?list=PLTZv4jL4go4Ql6aZFDi1KxXj2LIRawbgt}
\end{itemize}
\end{rSection}

\medskip



\end{rSection}




\begin{rSection}{Undergraduate Projects}

\begin{itemize}
    \item \textbf{Smart Surveillance System for Child and Elderly Care (Undergraduate Final Year Research Project)}
    \\Supervisors: Dr.S.A.H.A. Suraweera, Prof. M.P.B. Ekanayake, Prof. G.M.R.I. Godaliyadda
    \item \textbf{Wireless Sensor Based Automated Security System (This project was assigned in the third year of Undergraduate Studies)}
    
\end{itemize}
    
\end{rSection}

\begin{rSection}{Current Research}

\begin{itemize}


    \item During Fall 2022, I started to work on a problem introduced by G. Polya and G. Szego in their book "Isoperimetric Inequalities in Mathematical Physics" with my advisor. I have mentioned more details about my ongoing research in my \href{https://drive.google.com/file/d/1q9z3J-2oMmWdiA1qH06dD8iBnyTRSwW0/view?usp=share_link}{\color{red}{research statement}}.

    \item Starting from Spring 2023, I have been working on a problem related to the product of conformal radii of open sets having a fixed area. 
\end{itemize}

\end{rSection}

\begin{rSection}{Scholarships, Fellowships and Academic Awards}
\begin{itemize}
    \item Dr. Shelby Hildebrand Graduate Math Fellowship - Texas Tech University (2023-2024)
\end{itemize}
\end{rSection}


\begin{rSection}{Seminar Talks}
    \begin{itemize}
        \item "Product of Conformal Radii of open sets having a fixed area" - Analysis Seminar, Texas Tech University, April 24, 2023.
        \item "Product of Conformal Radii of open sets having a fixed area" - Analysis Seminar, Texas Tech University, November 13, 2023.
    \end{itemize}
\end{rSection}

\begin{rSection}{References}
\begin{itemize}
    \item Prof. Alexander Solynin
    \\ \textit{Department of Mathematics and Statistics, Texas Tech University, Texas, USA \\ Office : MA 231 \\
    Email: \href{mailto:alex.solynin@ttu.edu}{alex.solynin@ttu.edu}}

    \item Dr. Rochana Meegaskumbura
    \\ \textit{Department of Engineering Mathematics, University of Peradeniya, Sri Lanka 
    \\ Email: \href{mailto:rochanam@pdn.ac.lk}{rochanam@pdn.ac.lk}}
\end{itemize}
    
\end{rSection}






\end{document}
